### 2021-12-02 manuscript.tex
Outline WikidataBib results [ci skip]
This build is based on
https://github.com/lubianat/quali_phd/commit/2936776523ea1584882e2a08c3247194f8f4a1c7.

This commit was created by the following CI build and job:
https://github.com/lubianat/quali_phd/commit/2936776523ea1584882e2a08c3247194f8f4a1c7/checks
https://github.com/lubianat/quali_phd/actions/runs/1530897710

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/4244ca4800e49e86661876a45daa4ad73dc0ca6e/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/4244ca4800e49e86661876a45daa4ad73dc0ca6e}{lubianat/quali\_phd@4244ca4}
on December 2, 2021.

@@

\hypertarget{working-of-the-system}{%
\subsubsection{Working of the system}\label{working-of-the-system}}

It consists of a set of Python scripts and a standard file structure. A file contains the list of articles to be read in markdown. Articles are represented as Wikidata QIDs which enables automatic information retrieval from Wikidata's structured systems. Articles were organized in 2 main sections, one for cell-type related articles and one for biocuration-related articles.

The Wikidata Bib system has a ``pop'' function, which creates a personalized note document in markdown for the first article of a section and (if possible) obtains the full text article from Unpaywall (https://unpaywall.org/). The note document contains a space for highlights, which can be copied from the original text and pasted in the markdown file.
Notes and additional information are saved in a GitHub repository, and the structured information powers a live website with analytics on the users recent readings. The source code for Wikidata Bib is available at https://github.com/lubianat/wikidata\_bib/tree/template and notes on my readings can currently be accessed at https://lubianat.github.io/wikidata\_bib/.

@@

@@

\begin{itemize}
\tightlist
\item
  Total number of cells on Wikidata
\item
  Cells edited/added by me
\end{itemize}

>>>>

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/2936776523ea1584882e2a08c3247194f8f4a1c7/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/2936776523ea1584882e2a08c3247194f8f4a1c7}{lubianat/quali\_phd@2936776}
on December 2, 2021.

@@

\hypertarget{wikidata-bib-as-a-reading-system}{%
\subsection{Wikidata Bib as a reading system}\label{wikidata-bib-as-a-reading-system}}

It consists of a set of Python scripts and a standard file structure.
A file contains the list of articles to be read in markdown. Articles are represented as Wikidata QIDs which enables automatic information retrieval from Wikidata's structured systems.\\
Articles were organized in 2 main sections, one for cell-type related articles and one for biocuration-related articles.

\begin{itemize}
\tightlist
\item
  \textbf{Show file structure}
\end{itemize}

The Wikidata Bib system has a ``pop'' function, which creates a personalized note document in markdown for the first article of a section and (if possible) obtains the full text article from Unpaywall (https://unpaywall.org/).
The note document contains a space for highlights, which can be copied from the original text and pasted in the markdown file.

\begin{itemize}
\tightlist
\item
  \textbf{image pop}
\end{itemize}

Notes and additional information are saved in a GitHub repository, and the structured information powers a live website with analytics on the users recent readings.
The source code for Wikidata Bib is available at https://github.com/lubianat/wikidata\_bib/tree/template and notes on my readings can currently be accessed at https://lubianat.github.io/wikidata\_bib/.

\begin{itemize}
\item
  \textbf{image note-taking example}
\item
  \emph{Talk about Author Disambiguator and other contributions}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{image grep and open}
\end{itemize}

\hypertarget{wikidata-bib-as-a-dashboard}{%
\subsection{Wikidata Bib as a dashboard}\label{wikidata-bib-as-a-dashboard}}

\begin{itemize}
\item
  Wikidata Bib generates real-time, public visualizations of my literature progress
\item
  wbib package: https://github.com/lubianat/wbib
\item
  \textbf{Figures for queries}
\item
  \emph{Wikidata Bib reading status}:

  \begin{itemize}
  \tightlist
  \item
    articles read
  \item
    authors read
  \end{itemize}
\end{itemize}

\hypertarget{wikidata-bib-for-curation-of-cells-to-wikidata}{%
\subsection{Wikidata Bib for curation of cells to Wikidata}\label{wikidata-bib-for-curation-of-cells-to-wikidata}}

\begin{itemize}
\item
  Recording of cell types in Google Spreadsheets
\item
  Integration to Wikidata via Python script
\item
  Figure \ref{fig:biocuration_of_cells}
\end{itemize}

\begin{figure}
\hypertarget{fig:biocuration_of_cells}{%
\centering
\includegraphics[width=0.85\textwidth,height=\textheight]{images/extracting_cell_types.svg}
\caption{Wikidata Bib was coupled with a biocuration framework for cell types}\label{fig:biocuration_of_cells}
}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  Update the status via \url{https://colab.research.google.com/drive/1GvQXOs51_U8icdGMtKXMeLOXKM8pXWet\#scrollTo=szvBWI9zr_AA}
\end{itemize}

Wikidata statistics on cell types
2625 total cell classes
More than the Cell Ontology
519 human-specific cell classes
277 mouse-specific cell classes

User:TiagoLubiana:
At least 1 edit in 2495 cell classes
Created 1395 cell classes

\begin{figure}
\hypertarget{fig:subclass_of_cell}{%
\centering
\includegraphics[width=0.85\textwidth,height=\textheight]{https://keep.google.com/u/0/media/v2/1WoYkTz0M-ew_Tay-DpmOr2zyyCalnmsyd_2Ysq3pyNaJ7R5CIQnfdvZTDviBcvc/18W-amXz1489obuE7Tqb-AQHZKa-x-aVaH7QsO3x7Cy7lz-4a6AMzaGdLffzB?sz=512\&accept=image\%2Fgif\%2Cimage\%2Fjpeg\%2Cimage\%2Fjpg\%2Cimage\%2Fpng\%2Cimage\%2Fwebp}
\caption{Subclasses of ``cell'' on Wikidata}\label{fig:subclass_of_cell}
}
\end{figure}
